### 2023-09-11 main.tex
fix
lkj

This matrix is 

@@

%We have that 
%	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
%thus it is enough to look for a matrix $W$ such that 
%\begin{equation}\label{GoalWQ}
%	Q^{2L}W=WQ_{2L}^{0}
To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
	R(z,H):=\left(zI-H\right)^{-1}

@@

	(z-H)R(H,z)=1
In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$). We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We take $z=\Lambda_{\bm{m}}+\epsilon$ 
	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1

@@

	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We sum over all possible $m$ 
	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We take the limit for $\epsilon\to 0$ on both sides 

@@

Observe that 

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory. Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz. This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state. To write formula \eqref{W-extended} using the charges of the system, we the Quantum Inverse Scattering Method (QISM). We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$. 

@@

We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$

@@

The above matrices satisfy the following equations

@@

We define the \textit{transfer matrix}

@@

where we used the double row monodromy defined as

@@

This double row monodromy satisfies the following exchange relation

@@

This trasfer matrix has the following properties
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
	\begin{equation}\label{EX2}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
Then we have
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)
	\end{split}
\end{equation}
Therefore we can write the polynomial expansion
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
\begin{itemize}
	\item For the element $D_{N,N}(x)$: 
%The coefficients that we need are the following:
%\begin{equation}
%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
where 
\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
%\begin{equation}
%	\begin{split}
	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
%	\end{split}
%\end{equation}
\begin{comment}
{\color{blue}ok}

We observe that $\forall i,j=1,\ldots,N-1$
\begin{equation}
	\sum_{a\neq b}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	D_{N,N}^{2L-1}=e_{NN}^{tot}\left(2e_{NN}^{tot}+I^{tot}\right)-\sum_{j=1}^{N}e_{jj}^{tot}%=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}
Then

{\color{blue}ok?}where we used $
\sum_{i=1}^Ne_{ii}^{tot}=L$. 
\end{comment}
\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$ 
%\begin{equation}
%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{Dii-charge}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}
	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
\end{equation}
%\begin{equation}\label{a2lm1}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
%	\end{split}
%\end{equation}

%We rewrite
%\begin{equation}
%	\begin{split}
	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N%-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
%	\end{split}
%\end{equation}
%then
%\begin{equation}
%	\begin{split}
%		D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
%	\end{split}
%\end{equation}

>>>>

We will prove that 

@@

	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
\paragraph{Construction of matrix W}
We aim to show that \eqref{W-extended} fulfils \eqref{GoalWH}. Consider the \textit{resolvent operator}
	R(z,H^{''}):=\left(z-H^{''}\right)^{-1}

@@

	(z-H^{''})R(H^{''},z)=I
In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We chose $z=\Lambda_{\bm{m}}+\epsilon$ 
	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)=1

@@

	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
we sum over all possible $\bm{m}$'s 
	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
we multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
we take the limit for $\epsilon\to 0$ on both sides 

@@

Observe that, trivially,

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory. Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz. This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To write formula \eqref{W-extended} using the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM). We first present the simpler case of $gl(2)$, then we adapt the proof to the general $gl(N)$. 

@@

 We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$

@@

The above matrices satisfy

@@

We introduce the \textit{transfer matrix}

@@

that satisfies
The double row monodromy is given by

@@

$U_{0}(x)$ satisfies the following exchange relation

@@

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
\begin{comment}
	\begin{equation}
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			\vdots&\vdots&\ddots&\vdots\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
		\end{pmatrix}
	\end{equation}
\end{comment}
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	\end{pmatrix}
\end{equation}
The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
\begin{itemize}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
		\begin{split}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
		\end{split}	
	\end{equation}
	\begin{equation}\label{EX2}
		\begin{split}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
		\end{split}
	\end{equation}
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
		\begin{split}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			\\&+
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
		\end{split}
	\end{equation}

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
The transfer matrix $T^{\Delta}(x)$ reads
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)\\
	=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
	\end{split}
\end{equation}
therefore, it is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
where, for all $k\in\{0,\ldots,2L+2\}$, we call these $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}
Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
 Only the first three coefficients of the diagonal elements and the first coefficient of the non diagonal elements do survive when $x\to \infty$, therefore we only compute them. We obtain:
\begin{itemize}
	\item For $D_{N,N}(x)$:

\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}

\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$

\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{Dii-charge}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}
	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
\end{equation}

\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
\end{equation}

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three charges

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
By construction it follows that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where $\Delta_{i}=(\alpha_{i}-\beta_{i})$. 
Therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. However, this last non-diagonal term acts diagonally on the states. Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$ and it reads
